---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Introduction to fars

The `fars` package analyses data from the US National Highway Traffic Safety Administration's [Fatality Analysis Reporting System](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars), which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

## Summarize accidents

If you are interested in the number of accidents per month and year, you can count them with the `fars_summarize_years` function. You only need to provide the `years` of interest. The function will create the `filename`s using the `make_filename` function, read in the files from your current working directory using the `fars_read` function, and finally summarize the data.

```{r setup, include=FALSE}
require("knitr")
require("fars")
opts_knit$set(root.dir = system.file("extdata", package = "fars"))
```

```{r summarize, echo=TRUE}
fars_summarize_years(2013:2015)
```

## Map accidents

In order to display the point locations of accidents for a given state `state.num` and `year`, you can use the `fars_map_state` function.

```{r map, echo=TRUE}
fars_map_state(39, 2013)
```

[!Project status badge](https://ci.appveyor.com/api/projects/status/daovsxh32wuptc7t?svg=true)
