---
title: "Introduction to fars"
author: "L.S."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to fars}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `fars` package analyses data from the US National Highway Traffic Safety Administration's [Fatality Analysis Reporting System](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars), which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

## Summarize accidents

If you are interested in the number of accidents per month and year, you can count them with the `fars_summarize_years` function. You only need to provide the `years` of interest. The function will create the `filename`s using the `make_filename` function, read in the files from your current working directory using the `fars_read` function, and finally summarize the data.

```{r setup, include=FALSE}
require("knitr")
require("fars")
opts_knit$set(root.dir = system.file("extdata", package = "fars"))
```

```{r summarize, echo=TRUE}
fars_summarize_years(2013:2015)
```

## Map accidents

In order to display the point locations of accidents for a given state `state.num` and `year`, you can use the `fars_map_state` function.

```{r map, echo=TRUE}
fars_map_state(39, 2013)
```
